A deeper look into bug fixes: patterns, replacements, deletions, and additions

### 2016-02-15 MSRChallenge2016.tex
Added characteristic section

>>>>

\section{Results}

This section investigates how do developer fix bugs from three different
perspectives. To begin with, we show some characteristics of real-world bug
fixes.  Afterwards, we look deeper to find out what kinds of statements are
usually added, modified or deleted by human developers to fix bugs. Lastly, we
show how common PAR's fixing templates are in our dataset.

\subsection{Characteristics}

This subsection shows a bird's-eye view of real-world bug fixes at
ultra-large-scale. We did our analysis on the \emph{2015 September/Github}
dataset on Boa. This dataset includes $7,830,023$ Java projects with
$23,229,406$ revisions. Among all the revisions, $4,590,679$ revisions are
identified by Boa as bug fixing revisions. Our analysis in this subsection
focuses on these bug fixing revisions. We hope that this population
is big enough to reflect the bug fixing practice.

To begin with, we are interested in:

\begin{quote}
	How many files are changed to fix a bug?
\end{quote}

To answer this question, we identified all the bug fixing revisions in our
dataset and count the number of changed files. In total, $52,052,571$ files got
changed. Thus, on average each bug fixing revision changes 11.3 files.  This
number is surprisingly high because most automatic program repair techniques
assume that bugs are local in most cases. There could be several reasons behind
this number. It could be the case that other software artifacts (e.g.
documentation) are updated after bug fixing. It could also be the case that bug
fixing commit also contains changes that are not related to fixing bug (e.g. new
features, refactoring). To better understand why so many files are changed, we
continue to ask:

\begin{quote}
	What are the file types of those changed files?
\end{quote}

In Boa, each changed file is represented by a \emph{ChangedFile} node, and it
has a field called \emph{FileKind}, describing the type of each file.
Table~\ref{tbl:fileType} shows the file types that Boa could identify. To answer
this question, we iterate all the changed files in each bug fixing revision and
count the total number for each file type. Results are shown in
Table~\ref{tbl:fileType}.

\begin{table}
\centering
  \begin{tabular}{| c | r | r |}
  \hline
  File Kind & Total Number & Average \\ \hline \hline
  BINARY & 752,945 & 0.16 \\ \hline
  SOURCE\_JAVA\_ERROR & 2,073,558 & 0.45 \\ \hline
  SOURCE\_JAVA\_JLS2 & 2,607,413 & 0.57 \\ \hline
  SOURCE\_JAVA\_JLS3 & 15,748,967 & 3.43 \\ \hline
  SOURCE\_JAVA\_JLS4 & 83,798 & 0.02 \\ \hline
  TEXT & 541,023 & 0.12 \\ \hline
  XML & 6,818,299 & 1.49 \\ \hline
  UNKNOWN & 23426568 & 5.10 \\ \hline
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:fileType}
\end{table}

\emph{SOURCE\_JAVA\_ERROR} file kind represents files that Boa failed to parse.
\emph{JLS2} refers to Java files that are written in all versions of Java
languages up to and including J2SE 1.4. \emph{JLS3} refers to J2SE 1.5, and JLS4
refers to J2SE 1.6 and 1.7. Boa documentation does not explicitly explain what
is \emph{TEXT} and what is \emph{UNKNOWN}. Our assumption is that \emph{TEXT}
refers to files whose file name ends with ``.txt'', and \emph{UNKNOWN} refers to
all other kinds of files (e.g. .c file, .cpp files).

From Table~\ref{tbl:fileType}, we can see that \emph{TEXT} files and
\emph{BINARY} files are changed least frequently. This is not surprising because
\emph{TEXT} files are usually documentation files, and \emph{BINARY} files
should only be changed in rare case (e.g.  milestone, new release, dependency
update). If we consider all 4 kinds of Java files as one kind, then on average
each bug fixing revision changes $4.47$ Java files. But still, it does not
conform to our assumption of bug locality. \emph{XML} files in Java projects
usually represents build files, thus changing one build file after each bug
fixing is not surprising.  What surprises us is that \emph{UNKNOWN} files are
changed most frequently. Note that all the projects in our dataset are Java
projects, so it is reasonable to assume that these files are not source files
that written in other programming languages.  One possible explanation is that
they are test resources. However, due to the limitations of Boa, we can not look
into the content of these \emph{UNKNOWN} files.

Since Boa does not distinguish Java files that related to functionality and Java
files that related to testing, it could be the case that among those $4.47$
changed Java files, some of them are related to testing, such as modifying the
test cases and creating new test classes. To better understand what changes are
usually made to Java source code files, we continue to ask:

\begin{quote}
	How often do developers introduce new classes, methods, fields, variables in
	bug fixing commits?
\end{quote}

This research question is interesting because most automatic program repair
approaches could not create new classes/methods/fields/variables to fix bugs.
Most approaches guess and synthesize the patches based on existing source code.

Table~\ref{tbl:new} shows our analysis results. This table shows that
introducing new classes and new variables are rare. This is good news for
automatic program repair approaches. On average, we still have $0.69$ new method
per bug fix. If we consider the possibility of creating new test method (i.e.
methods that annotated by @Test if JUnit is used), this number is not that
scary. However, what surprises us is that $1.32$ fields are created per bug fix.
This indicates that automatic program repair approaches should pay attention to
the state of the class when fixing Java programs.

\begin{table}
\centering
  \begin{tabular}{| c | r | r |}
  \hline
  Introducing & Total Number & Average \\ \hline \hline
  Class & 729201 & 0.16 \\ \hline
  Methods & 3186867 & 0.69 \\ \hline
  Fields & 6076646 & 1.32 \\ \hline
  Variables & 924259 & 0.2 \\ \hline
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:new}
\end{table}
